BivData Setup

### 2020-01-22 doc/Main_Report_Results.rmd
first pass at analysis of Mixed models, outlined other predictions, made some notes in other files

@@

DF.HetC.MixedModel.pooled$sex <- factor(DF.HetC.MixedModel.pooled$sex, ordered = TRUE, levels =c("male", "female") )

@@

>>>>

todo, add the random effect tests, consider changing all to lmer() (those have better random effects)

@@

#consider changing to ordered = FALSE, for the DFs used for MM
DF.HetC.MixedModel.pooled$sex <- factor(DF.HetC.MixedModel.pooled$sex, ordered = TRUE, levels =c("male", "female") )

@@

```{r trackcurBivData, echo=FALSE}
#list / tally of current curated Bivdata
Cur_biv = read.csv("~./MLH1repo/data/CurrentCuratedDataset_13.1.20.csv", header = TRUE)

colnames(Cur_biv) <- c('mouse', 'blank','0','1')

AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages[ -c(9:12, 14, 18, 22:24) ]

AP_mouse_table_w.Ages_HQ <- add_sex(AP_mouse_table_w.Ages_HQ)
AP_mouse_table_w.Ages_HQ <- add_strain(AP_mouse_table_w.Ages_HQ)
AP_mouse_table_w.Ages_HQ <- add_category(AP_mouse_table_w.Ages_HQ)
AP_mouse_table_w.Ages_HQ <- add_subsp(AP_mouse_table_w.Ages_HQ)
AP_mouse_table_w.Ages_HQ <- add_species(AP_mouse_table_w.Ages_HQ)

#only M.musculus
AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[AP_mouse_table_w.Ages_HQ$species == "M.musculus",]
#REMOVE EXTRA STRAINS
AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[AP_mouse_table_w.Ages_HQ$subsp != "Cast",]
#remove musc strains
AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[AP_mouse_table_w.Ages_HQ$strain != "AST",]
AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[AP_mouse_table_w.Ages_HQ$strain != "TOM",]
#remove PERC, MOLF, CZECH, (no females)
AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[AP_mouse_table_w.Ages_HQ$strain != "CZECH",]
AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[AP_mouse_table_w.Ages_HQ$strain != "PERC",]
#156 mice (from 193)

#some mice are missing 13oct14

#match the MM dataset
AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[AP_mouse_table_w.Ages_HQ$Ncells > 9,]
AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[AP_mouse_table_w.Ages_HQ$age.weeks < 26,]
#126 mice

#AP_mouse_table_w.Ages_HQ <- AP_mouse_table_w.Ages_HQ[!(is.na(AP_mouse_table_w.Ages_HQ$mouse) | DF.HetC.MixedModel.HQ$mouse==""), ]

#mice missing from curated list
mice.within.BivData <- AP_mouse_table_w.Ages_HQ[ AP_mouse_table_w.Ages_HQ$mouse %in% Cur_biv$mouse, ]#54 mice in (14 mice have enteries but 0 curated biv)

#(14 mice need at least some curation

cur.data.mice <- Cur_biv[ Cur_biv$mouse %in% AP_mouse_table_w.Ages_HQ$mouse, ]

mice.missing.bivData <- AP_mouse_table_w.Ages_HQ[ ! AP_mouse_table_w.Ages_HQ$mouse %in% Cur_biv$mouse, ]#72 (includes mice not in MM)
#72 mice that I need to upload/run the algorithm on their images

#mice missing SC pass == '1'
colnames(Cur_biv) <- c("mouse","blank","SC.fail", "SC.pass")
NeedsCur <- Cur_biv[Cur_biv$SC.fail == 0,]

NeedsCur <- add_strain(NeedsCur)
write.table(NeedsCur, "~./MLH1repo/data/needs_cur.csv", sep=",",
            row.names = TRUE)

#44% of mice are missing curation

#write this table
write.table(OG.cURATE.table.mouse, "~./MLH1repo/data/CurrentCuratedDataset_13.1.20.csv", sep=",",
            row.names = TRUE)

mice.missing.bivData <- mice.missing.bivData[!(is.na(mice.missing.bivData$mouse) | mice.missing.bivData$mouse==""), ]
write.table(mice.missing.bivData, "~./MLH1repo/data/MissingMice_13.1.20.csv", sep=",",
            row.names = TRUE)

### 2020-01-22 src/BivData_Setup.Rmd
a few small notes from home
first pass at analysis of Mixed models, outlined other predictions, made some notes in other files

@@

>>>>

test work from home ()

add sis_co_ten  ref Lee 2019

format manual data set so SC.length = Chrmlength (matches the bivData)

add Q1 and Q4 to the cell summary stats table

for final dataset, drop levels of strains not used CZECG, AST, TOM, CAST,

@@

```{r clean.data, echo=FALSE, eval=FALSE}

Curated_BivData <- Curated_BivData[Curated_BivData$strain != "AST",]
Curated_BivData <- Curated_BivData[Curated_BivData$strain != "TOM",]
Curated_BivData <- Curated_BivData[Curated_BivData$strain != "CZECH",]

Curated_BivData <- droplevels(Curated_BivData$strain)
